Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-04-05 Paper/Paper.tex

\begin{figure}[ht]
\caption{Effect of any EHR Exposure on Retirement}
\vspace{2mm}
\centering
\hspace{20mm}
\includegraphics[scale=.45]{Objects/CS_retire_allEHR.pdf}
\vspace{3mm}
\newline
        \fbox{\begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/CS_retireold_allEHR.pdf}
        \end{minipage}}
        \hspace{0.1cm}
        \fbox{\begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/CS_retireyoung_allEHR.pdf}
        \end{minipage}}
        \label{fig:retirefirst}
\end{figure}

@@

\begin{figure}[ht]
\caption{Effect of any EHR Exposure on Likelihood of Working in Office}
\vspace{2mm}
\centering
\hspace{20mm}
\includegraphics[scale=.45]{Objects/CS_office_ind_allEHR.pdf}
\vspace{3mm}
\newline
        \fbox{\begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/CS_office_indold_allEHR.pdf}
        \end{minipage}}
        \hspace{0.1cm}
        \fbox{\begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/CS_office_indyoung_allEHR.pdf}
        \end{minipage}}
        \label{fig:officefirst}
\end{figure}

\begin{figure}[ht]
\caption{Effect of any EHR Exposure on Fraction of Patients in Office}
\vspace{2mm}
\centering
\hspace{20mm}
\includegraphics[scale=.45]{Objects/CS_office_frac_allEHR.pdf}
\vspace{3mm}
\newline
        \fbox{\begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/CS_office_fracold_allEHR.pdf}
        \end{minipage}}
        \hspace{0.1cm}
        \fbox{\begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/CS_office_fracyoung_allEHR.pdf}
        \end{minipage}}
        \label{fig:officesecond}
\end{figure}

Another way to examine whether physicians are switching settings in a vague sense is to see whether the zip codes in which the physicians work is changing. Estimates for this outcome variable are shown in

>>>>

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Retirement}
    \includegraphics[scale=.57]{Objects/retire_plot.pdf}
    \label{fig:retirefirst}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{obj}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}
Another way to examine whether physicians are switching settings in a vague sense is to see whether the zip codes in which the physicians work is changing. Estimates for this outcome variable are shown in
